`flippant` -- An `R` package for the automated analysis of dithionite scramblase

### 2015-09-21 inst/manuscript/manuscript.rmd
Fix citing details as provided by Birgit Ploier;
Clean up knittr options;
More careful multipanel figure formatting;

figure1 <- multipanelfigure(
  width = 17.22, 
  height = 18, 
  units = "cm", 
  columns = 2, 
  rows = 2)

knitr::opts_chunk$set(
  fig.width=6.78, 
  fig.height=6.78, 
  warning=FALSE, 
  message=FALSE,
  dev = 'pdf')
```

@@

#Funding
J.G., R.J.C. and the Proteomics Core at WCMC-Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medical College in Qatar, a program 
funded by Qatar Foundation. B.P. was supported by a grant from Qatar National 
Research Fund’s National Priority Research Program (5-669-1-112) to J.G. and
A.K.M.

>>>>

figure1 <- multipanelfigure(
  width = 17.22, 
  height = 18, 
  units = "cm", 
  columns = 2, 
  rows = 2,
  interPanelSpacing = 0.25)

knitr::opts_chunk$set(
  fig.width = 6.78, 
  fig.height = 7.09, 
  warning = FALSE, 
  message = FALSE)
```

@@

#Funding
J.G., R.J.C. and the Proteomics Core at WCMC-Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medical College in Qatar, a program 
funded by Qatar Foundation. B.P. was supported by a grant from Qatar National 
Research Fund’s National Priority Research Program (5-669-1-112) to J.G. and
A.K.M., as well as by the Austrian Science Fund (FWF), project J3686-B21.
